The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191014.tex
CIV tex/ tidy up

\begin{table*}
  \centering
  \begin{tabular}{l  lll  lll lll lll }
    \hline 
    \hline 
                    & \multicolumn{3}{l}{ {\bf J1205+3422}}          &  \multicolumn{6}{l}{{\bf J1638+2827}}                                                                                   &  \multicolumn{3}{l}{ {\bf J2228+2201}} \\
Emission      & \multicolumn{3}{l}{MJD 53498}                        & \multicolumn{3}{l}{MJD 54553}                        & \multicolumn{3}{l}{MJD 55832}                     &  \multicolumn{3}{l}{MJD 56189}     \\                 
line              & Line  $\sigma$ & Line  Flux &   Cont.  Flux   & Line  $\sigma$   & Line  Flux      & Cont.  Flux  & Line  $\sigma$ & Line  Flux  &   Cont. Flux  & Line  $\sigma$ & Line  Flux       &   Cont. Flux  \\    \hline                       
Ly$\alpha$  &   ---	        &	---      & ---                 &  1362	            &	510.5	    &	7.224          & 1769                 &  633.9	 &  5.376             & ---                   &  ---                & ---    \\
\nv	            & 1604	        & 1251        &  853.5             &  \; 854.6	    &	122.4   	    &	5.546          & 1012                 &  107.1	 &  4.645             &  5501	        &  611.3	          & -2.58  \\
$^{(a)}$\civ     & 2174	        & 1254	   &  661.6             &  1927	            &	462.6	    &	2.722         & 2287	               &  125.1	 &  1.256             &  2216	        & \; 48.67          &   0.49  \\
$^{(a)}$\heii    &  2174    	        & \;\; 33.2  &  620.3             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        &  \;\;\; 0.35      &   0.39  \\
$^{(a)}$\ciii     & 2174	        & \;  449.4  &  523.6             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        & \; 17.2             &  0.41  \\
$^{(a)}$\mgii   &  2174	        & \;	405.4  &  334.1             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        & \; 33.6	           &  0.29  \\
    \hline 
   \hline   
  \end{tabular}
  \caption{Line Measurement Information from the SDSS DR12 Science Archive Server (SAS). 
    %dr12.sdss.org/spectrumDetail?plateid=2089\&mjd=53498\&fiber=427 
    Line $\sigma$ in units of   km s$^{-1}$; 
    Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
    Continuum      in units of  10$^{-17}$ erg/cm$^2$/s/ \AA; 
    $^{(a)}$Emission lines of a common ``width group'', in this case,
    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
    the same intrinsic velocity width in the SDSS spectral line fitting
    procedure \citep{Bolton2012}.
  }
 \label{tab:SDSS_line_values}
\end{table*}

@@

>>>>

\begin{table*}
  \centering
  \begin{tabular}{l  lll  lll lll lll }
    \hline 
    \hline 
                      & \multicolumn{3}{l}{ {\bf J1205+3422}}          &  \multicolumn{6}{l}{{\bf J1638+2827}}                                                                                             &  \multicolumn{3}{l}{ {\bf J2228+2201}} \\
Emission         & \multicolumn{3}{l}{MJD 53498}                        & \multicolumn{3}{l}{MJD 54553}                            & \multicolumn{3}{l}{MJD 55832}                          &  \multicolumn{3}{l}{MJD 56189}     \\                 
line                 & Line  $\sigma$ & Line  Flux &   Cont.  Flux   & Line  $\sigma$   & Line  Flux      & Cont.  Flux      & Line  $\sigma$ & Line  Flux  &   Cont. Flux       & Line  $\sigma$ & Line  Flux       &   Cont. Flux  \\    \hline                    
Ly$\alpha$     &   ---	        &	---      & ---                   &  1362	            &	510.5	    &	7.224                 & 1769                 &  633.9	 &  5.376                 & ---                   &  ---                & ---    \\
\nv	               & 1604	        & 1251        &  853.5               &  \; 854.6	    &	122.4   	    &	5.546                 & 1012                 &  107.1	 &  4.645                 &  5501	        &  611.3	          & -2.58  \\
\civ $^{(a)}$     & 2174	        & 1254	   &  661.6                &  1927	            &	462.6	    &	2.722                 & 2287	               &  125.1	 &  1.256                 &  2216	        & \; 48.67          &   0.49  \\
\heii$^{(a)}$    &  2174            & \;\; 33.2  &  620.3               &  1927    	    & \;\;\; 8.067  &	2.447                 & 2287	               &  \; 10.7	 &  1.001                 &  2216	        &  \;\;\; 0.35      &   0.39  \\
\ciii$^{(a)}$     & 2174	        & \;  449.4  &  523.6               &  1927    	    & 164.6           &	1.966                 & 2287	               &  \; 29.5	 &  0.601                &  2216	        & \; 17.2             &  0.41  \\
\mgii $^{(a)}$   &  2174	        & \;	405.4  &  334.1              &  1927    	            & 187.4           &	1.513                 & 2287	               &  \; 34.7	 &  0.346                &  2216	        & \; 33.6	           &  0.29  \\
    \hline   
   \hline   
  \end{tabular}
  \caption{Line Measurement Information from the SDSS DR12 Science Archive Server (SAS). 
    %dr12.sdss.org/spectrumDetail?plateid=2089\&mjd=53498\&fiber=427 
    Line $\sigma$ in units of   km s$^{-1}$; 
    Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
    Continuum      in units of  10$^{-17}$ erg/cm$^2$/s/ \AA; 
    $^{(a)}$Emission lines of a common ``width group'', in this case,
    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
    the same intrinsic velocity width in the SDSS spectral line fitting
    procedure \citep{Bolton2012}. 
  }
 \label{tab:SDSS_line_values}
\end{table*}

@@

  % \begin{tabular}{lll  cccc r }
  \begin{tabu}{lll  cccc r }
    Object                               &   MJD       & line                        & Line  Lumin.          &  FWHM                         &  $V_{\rm off}$            & E.W.   &     Catalog  \\                                   
    % &                 &                                    &                           &                                   &                                       &          &     \\  
    \rowfont{\color{blue}}       & 53948            &  \civ                  &    570$\pm$14    &   9003$\pm$261          &  1487$\pm$76      &  18.09$\pm$0.46         &      \\
    \rowfont{\color{blue}}       &  {\it 53948 }   &  {\it \civ  }         &    ---                   &  {\it  5230$\pm$736}   &    ---                     &   {\it 30.1$\pm$1.21}  & {\it Shen2011}  \\
    \rowfont{\color{blue}}       &  {\it 53948 }   &  {\it \civ  }         &    {\it 1254}          &  {\it  5119}$^{(a)}$        &    ---                     &   ---                            & {\it SDSS DR12 SAS}  \\
                                              & 53948            &  \ciii                 &    467$\pm$15    &  13707$\pm$491         &  2983$\pm$223    &  25.90$\pm$0.84         &     \\
                                              & {\it 53948}     &  {\it \ciii}          &    {\it 449}            &   {\it  5119}$^{(a)}$        &  ---                       &                                    & {\it SDSS DR12 SAS}\\
    \rowfont{\color{teal}}        & 53948           &  \mgii               &    209$\pm$7       &     5063$\pm$175        &  -227$\pm$77       &  21.43$\pm$0.69      &     \\
 \multirow{2}{*}{{\bf J1205+3422}}  
                       &     \textcolor{teal}{53948}      &\textcolor{teal}{\mgii}   & \textcolor{teal}{405$\pm$7} & \textcolor{teal}{5063$\pm$175}   &  \textcolor{teal}{-227$\pm$77}   & \textcolor{teal}{21.43$\pm$0.69}        &     \\
    \rowfont{\color{teal}}        &  {\it 53948 }    &  {\it \mgii }        &   ---                    &   {\it  5119}$^{(a)}$       &    ---                     &   ---                           & {\it SDSS DR12 SAS }  \\ 
                                               \cdashline{2-8} 
    \rowfont{\color{blue}}       & 58538          &  \civ                    &      90$\pm$2      &   13112$\pm$208          &  1333$\pm$69      &   45.44$\pm$0.86     &     \\  
                                              & 58538          &  \ciii                    &      83$\pm$1      &   14913$\pm$245          &    942$\pm$93      &   52.99$\pm$0.91     &     \\  
    \rowfont{\color{teal}}        & 58538          &  \mgii                  &      71$\pm$2      &   14951$\pm$340          &    -63$\pm$129    &   77.08$\pm$1.69    &     \\
                                               \cdashline{2-8}
    \rowfont{\color{blue}}        & 58693          &  \civ                    &  1006$\pm$1     &   13685$\pm$127          &   3000                     &   17.19$\pm$0.17    &     \\  
                                              & 58693          &  \ciii                    &    151$\pm$1     &   15000                          &   3000                      &    39.31$\pm$0.24    &     \\  
    \rowfont{\color{teal}}          & 58693           &  \mgii                  &    180$\pm$1     &   11400$\pm$83           &     -82$\pm$34       &    73.71$\pm$0.50    &     \\  
                                               %& {\it  54553 }  &  {\it Ly$\alpha$}    &  {\it 510.5}          &  {\it  3207}$^{(a)}$        &    ---                        &   ---                             & {\it SDSS DR12 SAS}  \\
   \rowfont{\color{blue}}          & 54533             & \civ                  & 284$\pm$13       & 4574$\pm$658            &   55$\pm$438.31     &  31.80$\pm$1.51           &     \\
   \rowfont{\color{blue}}          &  {\it 54533 }    &  {\it \civ  }        &  ---                     &  {\it  4180$\pm$736}   &    ---                        &   {\it 100.5$\pm$11.9}  & {\it Shen2011}   \\
   \rowfont{\color{blue}}          &  {\it 54553 }    &  {\it \civ  }        &    {\it 462.6}          &  {\it  4537}$^{(a)}$         &    ---                       &   ---                              & {\it SDSS DR12 SAS}  \\

                                                & 54533             & \ciii                  & 105$\pm$7          & 3687$\pm$336            &  -246$\pm$122.7   &  33.29$\pm$2.32         &     \\
                                                & {\it 54553}     &  {\it \ciii}          &    {\it 164.6}            &   {\it  4537}$^{(a)}$        &  ---                         &  ---                           &  {\it SDSS DR12 SAS}\\  
    \rowfont{\color{teal}}           &  {\it 54533 }  &  {\it \mgii }        &   ---                    &  {\it 4802$\pm$2005}     &    ---                       &  {\it 115$\pm$33}         & {\it Shen2011}  \\
    \rowfont{\color{teal}}            &  {\it 54533 }  &  {\it \mgii }        &   {\it 187.4}          &  {\it 4537}$^{(a)}$             &    ---                       &  ---                           &  {\it SDSS DR12 SAS }  \\
                                                 \cdashline{2-8}
                                                  & 55832         & Ly$\alpha_{\rm na}$  &   27$\pm$4   &  783$\pm$102            & -323$\pm$35            &    9.72$\pm$1.59       &     \\   
                                                 & 55832          & Ly$\alpha$           & 288$\pm$11      &  4444$\pm$243           & -463$\pm$68           &  103.69$\pm$3.99     &     \\
                                                & {\it  55832 }  &  {\it Ly$\alpha$}    &  {\it 633.9}          &  {\it  4165.6}$^{(a)}$      &    ---                        &   ---                             & {\it SDSS DR12 SAS}  \\
\multirow{2}{*}{J1638+2827}
                & \textcolor{blue}{55832} & \textcolor{blue}{\civ}       &   \textcolor{blue}{73$\pm$3}     &  \textcolor{blue}{6253$\pm$259}   &  \textcolor{blue}{  270$\pm$106}     &  \textcolor{blue}{45.15$\pm$1.90}      &     \\
    \rowfont{\color{blue}}           &  {\it 55832 }  &  {\it \civ  }        &   -                          &  {\it  5210$\pm$226}   &    ---                       &    {\it 42.76$\pm$1.96 }     & {\it Ham17  }\\
    \rowfont{\color{blue}}           &  {\it 55832 }  &  {\it \civ  }       &    {\it 125.1}             &  {\it  5385.}$^{(a)}$        &    ---                       &   ---                             & {\it SDSS DR12 SAS}  \\
                                                 & 55832            & \ciii                &   19$\pm$6            & 14952$\pm$4682        &    3000$\pm$0         &   17.79$\pm$5.49      &     \\
                                                 & {\it 55832}     &  {\it \ciii}        &    {\it 10.68}            &   {\it  5385.}$^{(a)}$        &  ---                        &                                & {\it SDSS DR12 SAS}\\  
    \rowfont{\color{teal}}           & 55832            & \mgii               &  41$\pm$7             &        0$\pm$0              &    1000$\pm$1108     &    81.76$\pm$13.90    &     \\
    \rowfont{\color{teal}}           & {\it 55832}     &  {\it \mgii}      &    {\it 34.66}            &   {\it  5385.}$^{(a)}$        &  ---                       &                                & {\it SDSS DR12 SAS}\\  
                                                 \cdashline{2-8}
      \rowfont{\color{blue}}          & 58583             & \civ                 &  286$\pm$2         & -                                   &                   -                &   20.89$\pm$0.13      &     \\  
                                                & 58583            & \ciii                  &   92$\pm$1          &  6689$\pm$89             &    37$\pm$37.186        &   28.96$\pm$0.35      &     \\  
    \rowfont{\color{teal}}          & 58583            & \mgii               &  116$\pm$1          &  6649$\pm$85             & -422$\pm$34.818       &   67.38$\pm$0.77      &     \\  
    \rowfont{\color{blue}}         &  {\it 56189 }   &  {\it \civ }           &  {\it --- }               &  {\it 2994$\pm$620}    &     ---                        &  {\it 42.18$\pm$5.59}      &    {\it Ham17 } \\
    \rowfont{\color{blue}}          &  {\it 56189 }   &  {\it \civ  }         &    {\it 48.67}             &  {\it  5218}$^{(a)}$        &    ---                     &   ---                             & {\it SDSS DR12 SAS}  \\
                                                & 56189           & \ciii                           &  39$\pm$8      & 14097$\pm$2943        &   2243$\pm$1142    & 66.63$\pm$12.90     &     \\
                                                 & {\it 56189}     &  {\it \ciii}          &    {\it 17.2}            &   {\it  5218}$^{(a)}$           &  ---                       &                                & {\it SDSS DR12 SAS}\\  
    \rowfont{\color{teal}}           & 56189            & \mgii                         &  23$\pm$6          &   6694$\pm$1765   &   -597$\pm$741      & 41.19$\pm$10.95     &     \\
    \rowfont{\color{teal}}        & {\it 56189}     &  {\it \mgii}          &    {\it 33.6}            &   {\it  5218}$^{(a)}$           &  ---                       &                                & {\it SDSS DR12 SAS}\\  
                                                   \cdashline{2-8}
                                               & 56960    & Ly$\alpha_{\rm na}$   &   24$\pm$5         &     642$\pm$92               &    -319$\pm$30        &  2.71 $\pm$0.51      &     \\  
                                                & 56960    & Ly$\alpha$                & 121$\pm$38        & 3580$\pm$673              &     -16$\pm$171     &  13.52 $\pm$4.21    &     \\  
\multirow{2}{*}{J2228+2201}
           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}              & \textcolor{blue}{254$\pm$5}    &  \textcolor{blue}{8731$\pm$172}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{45.35$\pm$0.90}    &     \\   
                                               & 56960    & \ciii                            & 185$\pm$5           &        -                            &  2701$\pm$225         &   47.75$\pm$1.29    &     \\  
    \rowfont{\color{teal}}          & 56960    & \mgii                         &   99$\pm$4           &  7312.6$\pm$340        &   188$\pm$137          &   50.75$\pm$2.21     &     \\
                                            \cdashline{2-8}
     \rowfont{\color{blue}}        & 58693    & \civ                            & 54.688$\pm$0.6   &  6000.3$\pm$70           &      33$\pm$28          &   39.28$\pm$0.43     &     \\  
                                               & 58693    & \ciii                            & 115.08$\pm$1.2   & 15000                            &  2772$\pm$86          &   96.36$\pm$0.97     &     \\  
     \rowfont{\color{teal}}         & 58693    & \mgii                         & 46.361$\pm$1.3   & 8900$\pm$278             &  1000                         &   53.46$\pm$1.54     &     \\  
                                                %
     %    \end{tabular}
    \end{tabu}
\caption{Line Measurement Information from QSFIT, unless otherwise stated. 
      Shen11 is \citet{Shen2011}. 
      Ham17 is \citet{Hamann2017}.
      SDSS DR12 SAS is the line measurement information from the SDSS DR12
      Science Archive Server (SAS).
      $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
    }
 \label{tab: QSFIT_line_values}

\iffalse
  \begin{tabular}{lll  cccc r }
    Object                                 &   MJD       & line                        & Line  Lumin.      & FWHM                     &  $V_{\rm off}$            & E.W. \\                                 
    % &                 &                                    &                           &                               &                                  &        \\
                                               & 53948 &  \civ                            &    570$\pm$14  &     9003$\pm$261    &  1487$\pm$76      &  18.09$\pm$0.46  \\
                                               & 53948 &  \ciii                            &    467$\pm$15  &   13707$\pm$491    &  2983$\pm$223    &  25.90$\pm$0.84  \\
                                               & 53948 &  \mgii                          &    209$\pm$7    &     5063$\pm$175    &  -227$\pm$77     &  21.43$\pm$0.69  \\
                                               & 58538 &  \civ                             &      90$\pm$2    &   13112$\pm$208   &  1333$\pm$69      &   45.44$\pm$0.86   \\
\multirow{2}{*}{J1205+3422}  & 58538 &  \ciii                             &      83$\pm$1    &   14913$\pm$245   &    942$\pm$93      &   52.99$\pm$0.91  \\
                                               & 58538 &  \mgii                           &      71$\pm$2    &   14951$\pm$340   &    -63$\pm$129    &   77.08$\pm$1.69  \\
                                               & 58693 &  \civ                             &  1006$\pm$1    &   13685$\pm$127   &   3000                     &   17.19$\pm$0.17   \\
                                               & 58693 &  \ciii                             &    151$\pm$1    &   15000                   &   3000                      &    39.31$\pm$0.24  \\
                                               & 58693 &  \mgii                           &    180$\pm$1    &   11400$\pm$83    &     -82$\pm$34       &    73.71$\pm$0.50  \\
                                                 & 54533  & \civ                           & 284$\pm$13      & 4574$\pm$658       &      55$\pm$438.31   &  31.80$\pm$1.51    \\
                                                & 54533  & \ciii                           & 105$\pm$7        & 3687$\pm$336       &  -246$\pm$122.7      &  33.29$\pm$2.32    \\
                                                & 55832  & Ly$\alpha_{\rm na}$   &   27$\pm$4        &   783$\pm$102       & -323$\pm$35           &    9.72$\pm$1.59     \\ 
                                               & 55832  & Ly$\alpha$                & 288$\pm$11      &  4444$\pm$243       & -463$\pm$68            &  103.69$\pm$3.99   \\
\multirow{2}{*}{J1638+2827}   & 55832  & \civ                            &   73$\pm$3       &  6253$\pm$259       &    270$\pm$106         &    45.15$\pm$1.90    \\ 
                                                & 55832  & \ciii                           &   19$\pm$6        & 14952$\pm$4682    &    3000$\pm$0           &   17.79$\pm$5.49    \\
                                                 & 55832  & \mgii                         &  41$\pm$7         &        0$\pm$0          &    1000$\pm$1108    &   81.76$\pm$13.90  \\
                                                & 58583  & \civ                           & 286$\pm$2        & -                               &                   -               &   20.89$\pm$0.13    \\
                                                & 58583  & \ciii                           &  92$\pm$1         & 6689$\pm$89          &    37$\pm$37.186      &   28.96$\pm$0.35    \\
                                                & 58583  & \mgii                        & 116$\pm$1        & 6649$\pm$85           & -422$\pm$34.818     &   67.38$\pm$0.77    \\
                                               & 56189    & \ciii                           &  39$\pm$8          & 14097$\pm$2943     &   2243$\pm$1142    & 66.63$\pm$12.90   \\
                                               & 56189    & \mgii                         &  23$\pm$6          &   6694$\pm$1765     &   -597$\pm$741      & 41.19$\pm$10.95   \\
                                               & 56960    & Ly$\alpha_{\rm na}$   &   24$\pm$5         &     642$\pm$92        &    -319$\pm$30        &  2.71 $\pm$0.51    \\
                                               & 56960    & Ly$\alpha$                & 121$\pm$38        & 3580$\pm$673        &     -16$\pm$171     &  13.52 $\pm$4.21  \\
 \multirow{2}{*}{J2228+2201}  & 56960   & \civ                            & 254$\pm$5         &  8731$\pm$172       &        92$\pm$68      &   45.35$\pm$0.90  \\ 
                                               & 56960    & \ciii                           & 185$\pm$5          &        -                        &  2701$\pm$225     &   47.75$\pm$1.29  \\
                                               & 56960    & \mgii                         &   99$\pm$4          &  7312.6$\pm$340    &   188$\pm$137      &   50.75$\pm$2.21   \\
                                               & 58693    & \civ                           & 54.688$\pm$0.6   &  6000.3$\pm$70     &      33$\pm$28       &   39.28$\pm$0.43  \\
                                               & 58693    & \ciii                           & 115.08$\pm$1.2   & 15000                      &  2772$\pm$86       &   96.36$\pm$0.97   \\
                                               & 58693    & \mgii                         & 46.361$\pm$1.3   & 8900$\pm$278       &  1000                      &   53.46$\pm$1.54   \\
                                                %
  \caption{Line Measurement Information from QSFIT. }
 \label{tab: QSFIT_line_values}
\fi
